Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-07-01 ms.tex
Temporaty plots for Xcr and DM annihilation cross section. Place holder for integrated spectrum plot.

%%\section{Fermi-LAT Observations and Analysis}

@@

>>>>

\section{Fermi-LAT Observations and Analysis}

@@

\begin{figure*}
\begin{center}
%\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral flux upper limits (this work, Table X) compared with simulated integrated spectra of VHE gamma-ray emission from the Coma cluster.}
\label{fig:spectrum}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f5.eps}}
\end{center}
\caption{Cosmic-ray pressure, $X_{\mathrm{CR}}$, as a function of radial distance from the Coma cluster core.}
\label{fig:xcr}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f6.eps}}
\end{center}
\caption{Limits on the DM annihilation cross section $\expval{\sigma v}$ calculated using the VERITAS data in this work.}
\label{fig:dm}
\end{figure*}
